---
title: "Project 4"
output:
  pdf_document: default
  fontsize: 8pt
  html_document:
    df_print: paged
    fig_caption: yes
    number_sections: yes
---
<style type="text/css">

body{ /* Normal  */
      font-size: 18px;
  }

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE,message=FALSE,warning=FALSE)
```


Team ID: 3

Name (): Kieran Zhou

Name (): Liela Meng

Name (): Yunan Hou

Name (): Zhen Li

Github repo link:https://github.com/maoqunqun/STA207_project4.git

#  1.Introduction


# 2.Data analysis

## 2.1 Analysis plan

## 2.1.1 Exploratory data analysis  
 

```{r echo=F,message=FALSE}
library(ggplot2)
library(caret)
library(caretEnsemble)
library(ROSE)
library(mlbench)
library(DMwR)
library(rpart)
library(rattle)
library(rpart.plot)
library(RColorBrewer)
library(mlr)#for ugly table
```

The dataset has 41,188 rows and 21 columns.

The first 20 variables are our potential explanatory variables and the last one (“y”) is the dependent variable.

There are 12718 missing values in the dataset.

We can’t afford to delete 8,597 rows in our dataset, it’s more than 20% of our observations.(summary of missing value(can't run on windows, keep it or not?))
```{r, warning=F,fig.height=5 , fig.width=10}

#Load the dataset
setwd("C:\\Users\\yinan\\Desktop\\Project4\\bank")
data <- read.csv("bank-additional-full.csv",header=TRUE,sep=";")

#Summary on dataset
summary(datause)
dim(data)
names(data)
#ugly table
#summarizeColumns(data) %>% knitr::kable( caption = 'Feature Summary before Data Preprocessing')

#missing values
sum(data == "unknown")

#summary of missing value(can't run on windows, keep it or not?)
#data %>% 
#  summarise_all(list(~sum(. == "unknown"))) %>% 
#  gather(key = "variable", value = "nr_unknown") %>% 
#  arrange(-nr_unknown)
```

Exploratory Analysis

*用boxplot看每个continuous variable和y的关系
*用pie看每个discrete variable和y的关系（但是没做完，十个variable一个一个搞好麻烦，等个会写for循环的大佬搞定


```{r, warning=F,fig.height=5 , fig.width=10}

#continuous variable
par(mfrow=c(3,3))
p_age <- ggplot(data, aes(factor(y), age)) + geom_boxplot(aes(fill = factor(y)))
p_age

p_duration <- ggplot(data, aes(factor(y), duration)) + geom_boxplot(aes(fill = factor(y)))
p_duration

p_campaign <- ggplot(data, aes(factor(y), campaign)) + geom_boxplot(aes(fill = factor(y)))
p_campaign

p_pdays <- ggplot(data, aes(factor(y), pdays)) + geom_boxplot(aes(fill = factor(y)))
p_pdays

p_previous <- ggplot(data, aes(factor(y), previous)) + geom_boxplot(aes(fill = factor(y)))
p_previous

p_evr <- ggplot(data, aes(factor(y), data$emp.var.rate)) + geom_boxplot(aes(fill = factor(y)))
p_evr

p_ci <- ggplot(data, aes(factor(y), data$cons.price.idx)) + geom_boxplot(aes(fill = factor(y)))
p_ci

p_cci <- ggplot(data, aes(factor(y), data$cons.conf.idx)) + geom_boxplot(aes(fill = factor(y)))
p_cci

p_eb3 <- ggplot(data, aes(factor(y), data$euribor3m)) + geom_boxplot(aes(fill = factor(y)))
p_eb3

#discrete variable(unfinished)

data_yes<-data[data$y=="yes",]
data_no<-data[data$y=="no",]
dim(data_yes)
dim(data_no)
par(mfrow=c(10,2))

#marital 
label1<-paste(c("divorced","married ","single","unknown"),round(100*table(data_yes$marital)/4640),"%",sep=" ")
label2<-paste(c("divorced","married ","single","unknown"),round(100*table(data_no$marital)/36548),"%",sep=" ")
pie(table(data_yes$marital),label=label1,main="pie chart of marital")
pie(table(data_no$marital),label=label2,main="pie chart of marital")
#housing
label3<-paste(c("no","unknown","yes"),round(100*table(data_yes$housing)/4640),"%",sep=" ")
label4<-paste(c("no","unknown","yes"),round(100*table(data_no$housing)/36548),"%",sep=" ")
pie(table(data_yes$housing),label=label3,main="pie chart of housing")
pie(table(data_no$housing),label=label4,main="pie chart of housing")

```

Generate dummy variables


```{r, warning=F,fig.height=5 , fig.width=10}
#Generate dummy variables

data$Class<-factor(if_else(data$y == "yes", "1", "0"), levels = c("0", "1"))

for(level in unique(data$job)){
  data[paste("job", level, sep = "_")] <- ifelse(data$job == level, 1, 0)
}

for(level in unique(data$marital)){
  data[paste("marital", level, sep = "_")] <- ifelse(data$marital == level, 1, 0)
}

for(level in unique(data$education)){
  data[paste("education", level, sep = "_")] <- ifelse(data$education == level, 1, 0)
}

data$default_yes <- ifelse(data$default == "yes", 1, 0)

data$housing_yes <- ifelse(data$housing == "yes", 1, 0)

data$loan_yes <- ifelse(data$loan == "yes", 1, 0)

for(level in unique(data$contact)){
  data[paste("contact", level, sep = "_")] <- ifelse(data$contact == level, 1, 0)
}

for(level in unique(data$month)){
  data[paste("month", level, sep = "_")] <- ifelse(data$month == level, 1, 0)
}

for(level in unique(data$day_of_week)){
  data[paste("day", level, sep = "_")] <- ifelse(data$day_of_week == level, 1, 0)
}

for(level in unique(data$poutcome)){
  data[paste("poutcome", level, sep = "_")] <- ifelse(data$poutcome == level, 1, 0)
}

#Remove unwanted columns
data$X <- NULL
data$job <- NULL
data$marital <- NULL
data$education <- NULL
data$default <- NULL
data$housing <- NULL
data$loan <- NULL
data$contact <- NULL
data$month <- NULL
data$day_of_week<- NULL
data$poutcome <- NULL
data$y <- NULL

#correct variable name
data$Class <- as.factor((data$Class))
colnames(data)[15] <- "job_blue_collar"
colnames(data)[14] <- "job_admin"
colnames(data)[20] <- "job_self_employeed"
```
data Splitting (unfinished)

```{r, warning=F,fig.height=5 , fig.width=10}
#Splitting
set.seed(1)
training_size <- floor(0.80 * nrow(data))
train_ind <- sample(seq_len(nrow(data)), size = training_size)
training <- data[train_ind, ]
testing <- data[-train_ind, ]

#Normalizing(I do not know what the writer want to do since here,sorry)
preProcValues <- preProcess(training, method = c("center", "scale"))
scaled.training <- predict(preProcValues, training)
scaled.testing <- predict(preProcValues, testing)
```
### 2.1.2 Model




### 2.1.3 Hypothesis 




## 2.2 Analysis result

### 2.2.1 Model fitting result 



### 2.2.2 Hypothesis testing



### 2.2.3 Assumption satisfaction




# 3.Discussion

## 3.1 Conclusions and problems for further investigation



## 3.2 Causal inference



# 4.Reference

   